Report and Figures

### 2016-12-15 figs.Rmd
fix to clustering summary =

@@

```{r}
loss_curves %>% 
  group_by(city) %>% 
  filter(city %in% c('Atlanta', 'Philadelphia'),
         nclust %in% c(2, 5, 10)) %>% 
  mutate(I_XY = round(I_XY,2)) %>% 
  spread(key = city, value = I_XY, fill = NA) %>%
  write_csv('figs/clustering_summary.csv')
  # slice(match(nclust, c('2', '5', '10', 'I(X,Y)')))

>>>>

# check in here: are these binary clustering summaries? If so, we need to fix and get the full 
# clustering summaries instead.

@@

```{r}
loss_curves %>% 
  group_by(city) %>% 
  filter(city %in% c('Atlanta', 'Philadelphia'),
         nclust %in% c(2, 5, 10)) %>% 
  mutate(I_XY = round(I_XY,2)) %>% 
  select(city, I_XY, nclust) %>% 
  spread(key = city, value = I_XY, fill = NA) %>%
  write_csv('figs/clustering_summary.csv')
  # slice(match(nclust, c('2', '5', '10', 'I(X,Y)')))
